Verifying Demonstrations

### 2018-02-28 paper/DB-anon-cred.tex
Starts discussing related DB protocols
Makes DB anon creds a subsection, as it should
Updates bibsp, removes DBIV (it's public key anyway)
Improves discussion about DB and DBPK

\section{Distance bounding anonymous credentials}%
\label{DB-anon-cred}

\ProvideDocumentCommand{\DBPK}{m m}{\ensuremath{%
    \operatorname{DBPK}\mleft\{\mleft(#1\mright) : #2\mright\}%
  }}

We pointed out in \cref{DistanceBounding} that all security properties 
concerning \ac{DB} assume an \emph{honest} verifier.
This assumption does not hold in our setting, where every verifier at some point 
also might be a (malicious) prover.
We will introduce a new property for \ac{DB} protocols, the \ac{DBIV}.
Then we will propose a protocol that is \ac{DBIV}, \ac{DBMF}, \ac{DBDF}, 
\ac{DBDH} resistant but \emph{not} \ac{DBTF} resistant.
The protocol is based on the Schnorr identification scheme and thus allows us to 
do \ac{DB} \ac{ZKPK}, which allows us to form distance-bounding anonymous 
credentials.

\subsection{\Acl{DBIV} distance bounding}

\dots

\subsection{Reattempting \iacl{DB} Schnorr protocol}

@@

In the original \ac{DB} paper by \citet{DistanceBounding}, they proposed how to 
make the Schnorr identification scheme~\cite{Schnorr} distance bounding.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBIV}, \ac{DBMF}, \ac{DBDF} and \ac{DBDH}.
It will not protect against terrorist fraud, in fact, we suspect that \ac{DBIV} 
and \ac{DBTF} resistance are mutually exclusive.

We present the protocol in \cref{SchnorrFigure}.
The difference from the original Schnorr protocol is that the prover commits to 
two random values and the verifier sends two challenges.
Then the verifier decides which commitment and challenge to use in the \ac{DB} 
phase.

\begin{figure*}
  \centering
  \begin{tabular}{lcl}
    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[g, q, A]\):
    \\
    \toprule

@@

    % null
    &
    & Prepare \(B\in \bin^{k+l}\),
    \\

    % null
    &
    & with \(k\) bits set to \(b\)
    \\

    \midrule
    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < k+l\)} 
    \\

@@

    \bottomrule
  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
    \ac{DB} Schnorr protocol for \(\PK{\alpha}{A = g^\alpha}\).
    The protocol should be repeated in full to achieve the desired knowledge 
    error and distance-bounding error.
  }%
  \label{SchnorrFigure}
\end{figure*}

@@

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
phase for at least one round.
The verifier will send \(k+l < 2k\) challenges.
Thus the prover reveals the \(k\) bits of either \(s_0\) or \(s_1\) and only 
\(l\) bits of the other.
Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 
them from the prover.
But at this point the adversary must wait for \(b_{l+1}\) from the verifier and 
then relay that challenge to the prover to receive the correct \(r_i\) --- this 
relay will be detected.

>>>>

\subsection{Distance bounding anonymous credentials}%
\label{DB-anon-cred}

\ProvideDocumentCommand{\DBPK}{o o}{\ensuremath{%
    \operatorname{DBPK}%
    \IfValueT{#1}{%
      \IfValueTF{#2}{%
        \mleft\{\mleft(#1\mright) : #2\mright\}%
      }{%
        \mleft\{#1\mright\}%
      }%
    }%
  }}

We pointed out in \cref{DistanceBounding} that the majority of all \ac{DB} 
protocols that provide the above security properties assume an \emph{honest} 
verifier.
This assumption does not hold in our setting, where every verifier at some point 
also might be a (malicious) prover.
We thus need public-key \ac{DB}, and more specifically \ac{DBPK}.

There is a protocol which provide \ac{DBPK} with all the desired properties from 
above, ProProx~\cite{ProProx}.
(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
Knowledge.)
However, ProProx provides \iac{DBPK} protocol for quadratic residues, \ie for 
proving \(\DBPK[\alpha][a = \alpha^2]\).
We, on the other hand, need \iac{DBPK} protocol for discrete logarithms.
We will now introduce such a protocol which will allow us to do \ac{DB} 
anonymous credentials.
We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, 
\ac{DBDH} and \ac{DBIF} resistance --- \ie not \ac{DBTF} resistance.

\subsubsection{Reattempting \iacl{DB} Schnorr protocol}

@@

In the original \ac{DB} paper by \citet{DistanceBounding}, they proposed how to 
make the Schnorr identification scheme~\cite{Schnorr} distance bounding.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBIV}, \ac{DBMF}, \ac{DBDF} and \ac{DBDH}.
It will not protect against terrorist fraud, although this would be desirable.

We present the protocol in \cref{SchnorrFigure}.
The difference from the original Schnorr protocol is that the prover commits to 
two random values and the verifier sends two challenges.
Then the verifier presents to the prover which commitment and challenge to use 
during the \ac{DB} phase.

\begin{figure*}
  \centering
  \begin{tabular}{lcl}
    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[g, q, A]\):
    \\
    \midrule

@@

    % null
    &
    & Prepare \(B\in \bin^{\ceil{\log_2 q}+l}\),
    \\

    % null
    &
    & with \(\ceil{\log_2 q}\) bits set to \(b\)
    \\

    \midrule
    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < 
        \ceil{\log_2 q} + l\)} \\

@@

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
    \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
    The protocol should be repeated in full to achieve the desired knowledge 
    error and distance-bounding error.
  }%
  \label{SchnorrFigure}
\end{figure*}

@@

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
phase for at least one round.
The verifier will send \(\ceil{\log_2 q} + l < 2\ceil{\log_2 q}\) challenges.
Thus the prover reveals all the bits of either \(s_0\) or \(s_1\) but only \(l\) 
bits of the other.
Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 
them from the prover.
But at this point the adversary must wait for \(b_{l+1}\) from the verifier and 
then relay that challenge to the prover to receive the correct \(r_i\) --- this 
relay will be detected.
